---
title: "prediction ir mit hit"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---


#### Predicting individual responses to a MIT block and a HIT block: Mechanisms/characteristics underlying individual response variability
```{r}

# In this code chunk data is prepared for predictive/interaction analyses


```

## Session characteristics

#### % of VO2max during sessions 
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * rel.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()



figure <- data %>% 
  filter(period != "con", variable == "vo2.rel.max") %>%
  ggplot(aes(x=rel.vo2, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + # se = confidence intervals
  theme_pubr() +
  labs(x = expression("% of VO"["2max"]*"  during interval sessions (%) "), y = expression("∆ VO"["2max"]*"  ( mL ∙ min"^-1*" ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### Time > 90% of VO2max during sessions 
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * sec.90.vo2 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()


figure <- data %>% 
  filter(period != "con", variable == "vo2.rel.max") %>%
  ggplot(aes(x=sec.90.vo2, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = expression("Time > 90% of VO"["2max"]*"  during interval sessions (%) "), y = expression("∆ VO"["2max"]*"  ( mL ∙ min"^-1*" ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### % of HRmax during sessions 
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * rel.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### Time > 90% of HRmax during sessions 
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * sec.90.hr + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()


figure <- data %>% 
  filter(period != "con", variable == "ge.3.fresh") %>%
  ggplot(aes(x=sec.90.hr, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = expression("Time > 90% of VO"["2max"]*"  during interval sessions (%) "), y = expression("∆ VO"["2max"]*"  ( mL ∙ min"^-1*" ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### Total power input (kJ)
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * pi.total.kj + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()


figure <- data %>% 
  filter(period != "con", variable == "vo2.rel.max") %>%
  ggplot(aes(x=pi.total.kj, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = "Total power input (kJ)", y = expression("∆ VO"["2max"]*"  ( mL ∙ min"^-1*" ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

## Whole body characteristics

#### PO 40min cycling trial
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * w.rel.40tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### PO 15min cycling trial
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * w.rel.15tt + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

figure <- data %>% 
  filter(period != "con", variable == "ge.3.fresh") %>%
  ggplot(aes(x=w.rel.15tt, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = expression("PO"["15min"]*"  ( W ∙ kg"^-1*") at baseline"), y = "∆ GE (%-points)") +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### pVO2max at baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * w.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()



```

#### PO 4mmol/L [blood lactate]
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * w.rel.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### VO2max at baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * vo2.rel.max + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### % of VO2max at 4mmol baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * p.vo2.4mmol + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

figure <- data %>% 
  filter(period != "con", variable == "w.rel.15tt") %>%
  ggplot(aes(x=p.vo2.4mmol, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = expression("% of VO"["2max"]*"4mmol  at baseline (%) "), y = expression("∆ PO"["15min"]*"  ( W ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### GE at baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * ge.3.fresh + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### Isometric peak torque at 480 degrees/sec at baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * peak.torque.480 + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()


figure <- data %>% 
  filter(period != "con", variable == "w.rel.15tt") %>%
  ggplot(aes(x=peak.torque.480, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = "Isometric peak torque 480 d/s", y = expression("∆ PO"["15min"]*"  ( W ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

## Muscle characteristics
#### Muscle thickness (m. vastus lateralis, average of upper and lower part)
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * lat.avg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()


figure <- data %>% 
  filter(period != "con", variable == "w.rel.15tt") %>%
  ggplot(aes(x=lat.avg, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = "Muscle thickness m. vastus lateralis", y = expression("∆ PO"["15min"]*"  ( W ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### Lean mass legs (kg) at baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * lean.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### Fat free mass legs (kg) at baseline
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * fat.free.mass.legs + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

## Blood variables

#### Hemoglobin mass
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * hbmass.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()


figure <- data %>% 
  filter(period != "con", variable == "w.rel.4mmol") %>%
  ggplot(aes(x=hbmass.kg, y=change, color=period)) +
  geom_point() +
  geom_smooth(method="lm", se=TRUE, level = 0.95) + 
  theme_pubr() +
  labs(x = expression("Hb"["mass"]*"  ( g ∙ kg"^-1*") "), y = expression("∆ PO"["4mmol"]*"  ( W ∙ kg"^-1*") ")) +
  theme(text=element_text(family="serif", face="plain", size=11))
figure

```

#### Blood volume
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * bv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```

#### Plasma volume
```{r}

mod <- data %>%
  filter(period != "con", variable == "index") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.15tt") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.max") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "w.rel.4mmol") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "vo2.rel.max") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "p.vo2.4mmol") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

mod <- data %>%
  filter(period != "con", variable == "ge.3.fresh") %>%
  lmer(change ~ period * pv.kg + pre + (1 | id), data = .) %>%
  summ(confint = TRUE, digits = 3) %>% 
  print()

```
